FinalManuscript_DISCS_UG

### 2018-07-15 parts/02_relatedliterature.tex
Revised 2.2.1

\input{parts/02_relatedliterature_01homomorphiccryptosystems}

\section{Common Image Operations}
% skim chapters 3-4 of the book Digital Image Processing

% we may refer to the classification in the CryptoImg paper
Knowing that most of the common image operations rely on addition and multiplication operations, adopting a fully homomorphic cryptosystem enables image processing operations on encrypted images without the need of decryption.

In image processing, the typical image operations being done are intensity transformations which maps intensity values to another, and the use of spatial filters to do operations such as edge detection and image blurring.

\subsection{Intensity Transformation}
Intensity transformations are typically point operations, where a certain operation is applied to each single pixel of the image. Usually, there is a function $T$ that maps a pixel value $r$ into a new value $r^\prime$, thus this transformation satisfies the relation $r^\prime = T\left(r\right)$. Examples of intensity transformations are image negation, log transformation, and power-law transformation.

Image negation is an example of an intensity transformation, where the resulting image would be similar to a photographic negative~\cite{gonzalez_digital_2008}. In this case, suppose the intensity levels of an image are within the range $\left[0, L-1\right]$, then image negation can be expressed by
\begin{equation}
    T\left(r\right) = L-1-r
\end{equation}

The log transformation is used to enhance dark pixels or increase the dark details of an image by mapping low intensity values to a wider range of values~\cite{gonzalez_digital_2008}. This has the general form
\begin{equation}
    T\left(r\right) = c \log\left(1 + r\right)
\end{equation}
where $c$ is a constant and $r \ge 0$.

The power-law transformation is a family of transformations that have the form
\begin{equation}
    T\left(r\right) = c r^{\gamma}
\end{equation}
where $c>0$ and $\gamma > 0$. This is especially useful since many output devices such as printers and display devices follow the power law, and so correcting the power-law response on these devices in a process called \textit{gamma correction} ensures reproducibility and accuracy of images being displayed~\cite{gonzalez_digital_2008}.

\subsection{Edge Detection and Spatial Filtering}
Edge detection is used to find and determine the boundaries in an image, commonly used in applications such as image segmentation and feature extraction. This works by detecting so-called \textit{edges}, areas that have abrupt changes in intensity.

Edge detection is usually done by using gradient operators that detect such abrupt changes. These operators are commonly known as \textit{spatial filter}, which are usually of $3 \times 3$ size. A common example of spatial filters is the Sobel operator, with two matrices (also called as kernels) $g_x$ and $g_y$ representing the horizontal and vertical components respectively.
\begin{equation}
    g_x =
    \begin{bmatrix}
        -1 & 0 & 1 \\
        -2 & 0 & 2 \\
        -1 & 0 & 1
    \end{bmatrix}
    \qquad\text{and}\qquad
    g_y =
    \begin{bmatrix}
        1 & 2 & 1 \\
        0 & 0 & 0 \\
        -1 & -2 & -1
    \end{bmatrix}
\end{equation}
To get the resulting image $I^\prime$, a convolution is performed between the original image $I$ of size $M \times N$ and the kernel $k$ of size $m \times n$. Now suppose that the pixel value of an image at point $\left(i,j\right)$ is $r_{i,j}$. Then, a transformation using spatial filters can be described as follows:
\begin{align}
    T\left(r_{i,j}\right) &= \left[k * I\right]\left(\left\lfloor\frac{m}{2}\right\rfloor, \left\lfloor\frac{n}{2}\right\rfloor \right) \\
                         &= \sum_{u=1}^{m} \sum_{v=1}^{n} \left[k_{i,j} r_{i+u, j+v} \right]
\end{align}

Spatial filters are not only used for edge detection, but there are also filters that do image smoothing (such as Gaussian blur and box blur, $b_g$ and $b$ respectively in Equation~\ref{eqn:smooth-filters}) and image sharpening, to name a few \cite{gonzalez_digital_2008}.
\begin{equation}
    \label{eqn:smooth-filters}
    b_g = \frac{1}{16}
    \begin{bmatrix}
        1 & 2 & 1 \\
        2 & 4 & 2 \\
        1 & 2 & 1
    \end{bmatrix}
    \qquad
    b = \frac{1}{9}
    \begin{bmatrix}
        1 & 1 & 1 \\
        1 & 1 & 1 \\
        1 & 1 & 1
    \end{bmatrix}
\end{equation}
% Should I put a table of other kernels too?

>>>>

\input{parts/02_relatedliterature_01homomorphiccryptosystems}
\input{parts/02_relatedliterature_02commonimageprocessingoperations}
